---
output:
  html_document: default
  word_document: default
  pdf_document: default
---


```{r}
library(ggpmisc)
#set.seed(21318)
#df <- data.frame(x = c(1:100))
#df$y <- 2 + 3*df$x + rnorm(100, sd = 40)

formula1 <- y ~ poly(x, 2)
df <- iris |>
  rename(x=Sepal.Length, 
         y =Sepal.Width)
ggplot(data = df, aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, formula = formula1) +
  stat_fit_tb(method = "lm",
              method.args = list(formula = formula1),
              tb.vars = c(Parameter = "term", 
                          Estimate = "estimate", 
                          "s.e." = "std.error", 
                          "italic(t)" = "statistic", 
                          "italic(P)" = "p.value"),
              label.y = "bottom", label.x = "right",
              parse = TRUE) +
  stat_poly_eq(aes(label = paste0("atop(", ..eq.label.., ",", ..rr.label.., ")")), 
               formula = formula1, 
               parse = TRUE) +
  theme_bw(base_size = 16)
```

```{r}
library(ggpubr)
df3 <- ToothGrowth
p <- ggbarplot(df3, x = "dose", y = "len", fill = "supp",
 add = "mean_se", palette = c("#00AFBB", "#E7B800"), lab.vjust = -0.7,
 lab.hjust = 1.3,
 label = TRUE,
 position = position_dodge(), ggtheme = theme_bw())
#ggplotly(p) 
p
```


```{r}
library(ggstatsplot)
p2 <- ggbetweenstats(mtcars, am, mpg, ggtheme = ggthemes::theme_fivethirtyeight(), bf.prior = NULL, outlier.tagging = TRUE,
                     outlier.color = "blue")
p2
```


```{r}
summary(lm(am ~ mpg, mtcars))
```



```{r}
#lm(am ~ mpg, mtcars)

test <- t.test(mpg ~ am, mtcars, alternative = "two.sided") 
report::report(test)
#report(sessionInfo())
```

We fitted a linear model (estimated using OLS) to predict am with mpg
(formula: am ~ mpg). The model explains a statistically significant and
substantial proportion of variance (R2 = 0.36, F(1, 30) = 16.86, p < .001,
adj. R2 = 0.34). The model's intercept, corresponding to mpg = 0, is at -0.59
(95% CI [-1.11, -0.07], t(30) = -2.33, p = 0.026). Within this model:

  - The effect of mpg is statistically significant and positive (beta = 0.05,
95% CI [0.02, 0.07], t(30) = 4.11, p < .001; Std. beta = 0.60, 95% CI [0.30,
0.90])

Standardized parameters were obtained by fitting the model on a standardized
version of the dataset. 95% Confidence Intervals (CIs) and p-values were
computed using a Wald t-distribution approximation.
Warning: Unable to retrieve data from htest object. Using t_to_d() approximation.Effect sizes were labelled following Cohen's (1988) recommendations.

The Welch Two Sample t-test testing the difference of mpg by am (mean in
group 0 = 17.15, mean in group 1 = 24.39) suggests that the effect is
negative, statistically significant, and large (difference = -7.24, 95% CI
[-11.28, -3.21], t(18.33) = -3.77, p = 0.001; Cohen's d = -1.76, 95% CI
[-2.82, -0.67])
Analyses were conducted using the R Statistical language (version 4.2.1; R
Core Team, 2022) on macOS Monterey 12.5.1, using the packages keras (version
2.9.0; Allaire J, Chollet F, 2022), rsconnect (version 0.8.26; Atkins A et
al., 2022), shinyjs (version 2.1.0; Attali D, 2021), infer (version 1.0.0;
Bray A et al., 2021), shinythemes (version 1.2.0; Chang W, 2021),
shinydashboard (version 0.7.2; Chang W, Borges Ribeiro B, 2021), shiny
(version 1.7.2; Chang W et al., 2022), xgboost (version 1.6.0.1; Chen T et
al., 2022), htmltools (version 0.5.3; Cheng J et al., 2022),
shinydashboardPlus (version 2.0.3; Granjon D, 2021), lubridate (version
1.8.0; Grolemund G, Wickham H, 2011), purrr (version 0.3.4; Henry L, Wickham
H, 2020), kernlab (version 0.9.31; Karatzoglou A et al., 2022), ggpubr
(version 0.4.0; Kassambara A, 2020), modeldata (version 0.1.1; Kuhn M, 2021),
caret (version 6.0.92; Kuhn M, 2022), tune (version 0.2.0; Kuhn M, 2022),
workflowsets (version 0.2.1; Kuhn M, 2022), dials (version 0.1.1; Kuhn M,
Frick H, 2022), yardstick (version 0.0.9; Kuhn M, Vaughan D, 2021), parsnip
(version 0.2.1; Kuhn M, Vaughan D, 2022), tidymodels (version 0.2.0; Kuhn M,
Wickham H, 2020), recipes (version 0.2.0; Kuhn M, Wickham H, 2022), bsplus
(version 0.1.3; Lyttle I, 2021), report (version 0.5.5; Makowski D et al.,
2021), shinyFeedback (version 0.4.0; Merlino A, Howard P, 2021), tibble
(version 3.1.7; Müller K, Wickham H, 2022), ggstatsplot (version 0.9.4; Patil
I, 2021), shinyWidgets (version 0.7.0; Perrier V et al., 2022), broom
(version 0.8.0; Robinson D et al., 2022), shinycssloaders (version 1.0.0;
Sali A, Attali D, 2020), lattice (version 0.20.45; Sarkar D, 2008), rsample
(version 0.1.1; Silge J et al., 2021), compositions (version 2.0.4; van den
Boogaart KG et al., 2022), workflows (version 0.2.6; Vaughan D, 2022),
ggplot2 (version 3.3.6; Wickham H, 2016), stringr (version 1.4.0; Wickham H,
2019), forcats (version 0.5.1; Wickham H, 2021), tidyverse (version 1.3.1;
Wickham H et al., 2019), dplyr (version 1.0.9; Wickham H et al., 2022), tidyr
(version 1.2.0; Wickham H, Girlich M, 2022), readr (version 2.1.2; Wickham H
et al., 2022), scales (version 1.2.0; Wickham H, Seidel D, 2022) and DT
(version 0.23; Xie Y et al., 2022).

References
----------
  - Allaire J, Chollet F (2022). _keras: R Interface to 'Keras'_. Rpackage
version 2.9.0, <https://CRAN.R-project.org/package=keras>.
  - Atkins A, McPherson J, Allaire J (2022). _rsconnect: DeploymentInterface
for R Markdown Documents and Shiny Applications_. R packageversion 0.8.26,
<https://CRAN.R-project.org/package=rsconnect>.
  - Attali D (2021). _shinyjs: Easily Improve the User Experience of YourShiny
Apps in Seconds_. R package version
2.1.0,<https://CRAN.R-project.org/package=shinyjs>.
  - Bray A, Ismay C, Chasnovski E, Couch S, Baumer B, Cetinkaya-Rundel M(2021).
_infer: Tidy Statistical Inference_. R package version
1.0.0,<https://CRAN.R-project.org/package=infer>.
  - Chang W (2021). _shinythemes: Themes for Shiny_. R package version1.2.0,
<https://CRAN.R-project.org/package=shinythemes>.
  - Chang W, Borges Ribeiro B (2021). _shinydashboard: Create Dashboardswith
'Shiny'_. R package version
0.7.2,<https://CRAN.R-project.org/package=shinydashboard>.
  - Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie Y, Allen
J,McPherson J, Dipert A, Borges B (2022). _shiny: Web ApplicationFramework
for R_. R package version 1.7.2,<https://CRAN.R-project.org/package=shiny>.
  - Chen T, He T, Benesty M, Khotilovich V, Tang Y, Cho H, Chen K,Mitchell R,
Cano I, Zhou T, Li M, Xie J, Lin M, Geng Y, Li Y, Yuan J(2022). _xgboost:
Extreme Gradient Boosting_. R package version1.6.0.1,
<https://CRAN.R-project.org/package=xgboost>.
  - Cheng J, Sievert C, Schloerke B, Chang W, Xie Y, Allen J (2022)._htmltools:
Tools for HTML_. R package version
0.5.3,<https://CRAN.R-project.org/package=htmltools>.
  - Granjon D (2021). _shinydashboardPlus: Add More 'AdminLTE2'Components to
'shinydashboard'_. R package version
2.0.3,<https://CRAN.R-project.org/package=shinydashboardPlus>.
  - Grolemund G, Wickham H (2011). “Dates and Times Made Easy withlubridate.”
_Journal of Statistical Software_, *40*(3),
1-25.<https://www.jstatsoft.org/v40/i03/>.
  - Henry L, Wickham H (2020). _purrr: Functional Programming Tools_. Rpackage
version 0.3.4, <https://CRAN.R-project.org/package=purrr>.
  - Karatzoglou A, Smola A, Hornik K (2022). _kernlab: Kernel-BasedMachine
Learning Lab_. R package version
0.9-31,<https://CRAN.R-project.org/package=kernlab>.Karatzoglou A, Smola A,
Hornik K, Zeileis A (2004). “kernlab - An S4Package for Kernel Methods in R.”
_Journal of Statistical Software_,*11*(9), 1-20.
doi:10.18637/jss.v011.i09<https://doi.org/10.18637/jss.v011.i09>.
  - Kassambara A (2020). _ggpubr: 'ggplot2' Based Publication ReadyPlots_. R
package version 0.4.0,<https://CRAN.R-project.org/package=ggpubr>.
  - Kuhn M (2021). _modeldata: Data Sets Used Useful for ModelingPackages_. R
package version 0.1.1,<https://CRAN.R-project.org/package=modeldata>.
  - Kuhn M (2022). _caret: Classification and Regression Training_. Rpackage
version 6.0-92, <https://CRAN.R-project.org/package=caret>.
  - Kuhn M (2022). _tune: Tidy Tuning Tools_. R package version
0.2.0,<https://CRAN.R-project.org/package=tune>.
  - Kuhn M (2022). _workflowsets: Create a Collection of
'tidymodels'Workflows_. R package version
0.2.1,<https://CRAN.R-project.org/package=workflowsets>.
  - Kuhn M, Frick H (2022). _dials: Tools for Creating Tuning ParameterValues_.
R package version 0.1.1,<https://CRAN.R-project.org/package=dials>.
  - Kuhn M, Vaughan D (2021). _yardstick: Tidy Characterizations of
ModelPerformance_. R package version
0.0.9,<https://CRAN.R-project.org/package=yardstick>.
  - Kuhn M, Vaughan D (2022). _parsnip: A Common API to Modeling andAnalysis
Functions_. R package version
0.2.1,<https://CRAN.R-project.org/package=parsnip>.
  - Kuhn M, Wickham H (2020). _Tidymodels: a collection of packages formodeling
and machine learning using tidyverse
principles._.<https://www.tidymodels.org>.
  - Kuhn M, Wickham H (2022). _recipes: Preprocessing and FeatureEngineering
Steps for Modeling_. R package version
0.2.0,<https://CRAN.R-project.org/package=recipes>.
  - Lyttle I (2021). _bsplus: Adds Functionality to the R Markdown +Shiny
Bootstrap Framework_. R package version
0.1.3,<https://CRAN.R-project.org/package=bsplus>.
  - Makowski D, Ben-Shachar M, Patil I, Lüdecke D (2021). “AutomatedResults
Reporting as a Practical Tool to Improve Reproducibility andMethodological
Best Practices Adoption.” _CRAN_.<https://github.com/easystats/report>.
  - Merlino A, Howard P (2021). _shinyFeedback: Display User Feedback inShiny
Apps_. R package version
0.4.0,<https://CRAN.R-project.org/package=shinyFeedback>.
  - Müller K, Wickham H (2022). _tibble: Simple Data Frames_. R packageversion
3.1.7, <https://CRAN.R-project.org/package=tibble>.
  - Patil I (2021). “Visualizations with statistical details: The'ggstatsplot'
approach.” _Journal of Open Source Software_, *6*(61),3167.
doi:10.21105/joss.03167
<https://doi.org/10.21105/joss.03167>,<https://doi.org/10.21105/joss.03167>.
  - Perrier V, Meyer F, Granjon D (2022). _shinyWidgets: Custom InputsWidgets
for Shiny_. R package version
0.7.0,<https://CRAN.R-project.org/package=shinyWidgets>.
  - R Core Team (2022). _R: A Language and Environment for
StatisticalComputing_. R Foundation for Statistical Computing, Vienna,
Austria.<https://www.R-project.org/>.
  - Robinson D, Hayes A, Couch S (2022). _broom: Convert StatisticalObjects
into Tidy Tibbles_. R package version
0.8.0,<https://CRAN.R-project.org/package=broom>.
  - Sali A, Attali D (2020). _shinycssloaders: Add Loading Animations toa
'shiny' Output While It's Recalculating_. R package version
1.0.0,<https://CRAN.R-project.org/package=shinycssloaders>.
  - Sarkar D (2008). _Lattice: Multivariate Data Visualization with
R_.Springer, New York. ISBN
978-0-387-75968-5,<http://lmdvr.r-forge.r-project.org>.
  - Silge J, Chow F, Kuhn M, Wickham H (2021). _rsample: GeneralResampling
Infrastructure_. R package version
0.1.1,<https://CRAN.R-project.org/package=rsample>.
  - van den Boogaart KG, Tolosana-Delgado R, Bren M (2022)._compositions:
Compositional Data Analysis_. R package version
2.0-4,<https://CRAN.R-project.org/package=compositions>.
  - Vaughan D (2022). _workflows: Modeling Workflows_. R package version0.2.6,
<https://CRAN.R-project.org/package=workflows>.
  - Wickham H (2016). _ggplot2: Elegant Graphics for Data
Analysis_.Springer-Verlag New York. ISBN
978-3-319-24277-4,<https://ggplot2.tidyverse.org>.
  - Wickham H (2019). _stringr: Simple, Consistent Wrappers for CommonString
Operations_. R package version
1.4.0,<https://CRAN.R-project.org/package=stringr>.
  - Wickham H (2021). _forcats: Tools for Working with CategoricalVariables
(Factors)_. R package version
0.5.1,<https://CRAN.R-project.org/package=forcats>.
  - Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R,Grolemund G,
Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, MillerE, Bache SM, Müller K,
Ooms J, Robinson D, Seidel DP, Spinu V,Takahashi K, Vaughan D, Wilke C, Woo
K, Yutani H (2019). “Welcome tothe tidyverse.” _Journal of Open Source
Software_, *4*(43), 1686.doi:10.21105/joss.01686
<https://doi.org/10.21105/joss.01686>.
  - Wickham H, François R, Henry L, Müller K (2022). _dplyr: A Grammar ofData
Manipulation_. R package version
1.0.9,<https://CRAN.R-project.org/package=dplyr>.
  - Wickham H, Girlich M (2022). _tidyr: Tidy Messy Data_. R packageversion
1.2.0, <https://CRAN.R-project.org/package=tidyr>.
  - Wickham H, Hester J, Bryan J (2022). _readr: Read Rectangular TextData_. R
package version 2.1.2,<https://CRAN.R-project.org/package=readr>.
  - Wickham H, Seidel D (2022). _scales: Scale Functions forVisualization_. R
package version 1.2.0,<https://CRAN.R-project.org/package=scales>.
  - Xie Y, Cheng J, Tan X (2022). _DT: A Wrapper of the JavaScriptLibrary
'DataTables'_. R package version
0.23,<https://CRAN.R-project.org/package=DT>.


